\texttt{\df} -- \\ modifying drafted figures\footnote{ For further information about the code visit \href{https://github.com/LukasCBossert/draftfigure}{https://github.com/LukasCBossert/draftfigure} Comments and criticisms are welcome.}

### 2017-05-07 draftfigure.tex
done version 0.1

% \draftfigure --%
%            modifying drafted figures
% Copyright (c) 2017 Lukas C. Bossert
%  
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
% !TEX program = lualatex
\documentclass[a4paper,
12pt,
english
]{ltxdoc}

\input{draftfigure-preamble.tex}
\newcommand\df{draftfigure\xspace}
\newcommand\dfstring{|draftfigure|\xspace}
\setkeys{Gin}{width=.4\linewidth}

@@

%\begin{multicols}{1}
\footnotesize\parskip=0mm \tableofcontents
%\end{multicols}

@@

If you do not like the outcome with the filename and its path written with |\ttfamily| then use this package \dfstring to modify the outcome.
\clearpage

@@

\begin{code}
\usepackage[%
  *@\meta{further options}@*
  ]{draftfigure}
\end{code}
Without any further options you will now get white boxes instead of the images.
\begin{examplebox}
\begin{figure}[H]\setkeys{Gin}{draft=true}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
The size of the boxes are identical to the size of the images which you can define optionally with |[width=.3\linewidth]|
\clearpage

@@

So let’s see some action.
\subsection{Preamble}
The following options are set in the preamble and considered globally for all figures.
\subsubsection{content}
\DescribeMacro{content}
With this option you can set an individual text which will be displayed in the white box.
\begin{code}
\usepackage[%
  content = {This figure is omitted due to missing copyrights.},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{draftfigure}{content = {This figure is omitted due to missing copyrights.}}
	\setkeys{Gin}{draft=true}
  \centering
  \includegraphics[width=.4\linewidth]{example-image-a}
  \caption{A}
  \includegraphics[width=.4\linewidth]{example-image-b}
  \caption{B}
\end{figure}
\end{examplebox}
\clearpage
\subsubsection{filename}
\DescribeMacro{filename}
Activating this option with |true| the filename will be displayed in the white box.
If you also have defined some text for |content| the filename will appear one line below of |content|.
\begin{code}
\usepackage[%
  filename,%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{filename}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
\clearpage
And with some text in |content| it will look like this:
\begin{code}
\usepackage[%
  filename,%
  content={no image available}
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{filename,
	content={no image available}}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
\clearpage
\subsubsection{style}
\DescribeMacro{style} This defines the font style of the text of |content| or |filename|. 
You can chose one of the following styles: 
\begin{itemize}
	\item[sf] |\sffamily|
	\item[tt] |\ttfamily|
	\item[rm] |\rmfamily|
	\item[normal] |\normalfont|
	\item[bf] |\bfseries|
	\item[it] |\itshape|
	\item[sc] |\scshape|
\end{itemize}
Default is |sf|.
\begin{code}
\usepackage[%
  content={hidden image},
  style = {bf},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{style={bf},content={hidden image}}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  % \includegraphics{example-image-c}
 %  \caption{C}
\end{figure}
\end{examplebox}
\clearpage
\subsubsection{size}
\DescribeMacro{size}
You can also define the text size of |content| with predefined values: 
\begin{itemize}
	\item[tiny] |\tiny|
	\item[scriptsize] |\scriptsize|
	\item[small] |\small|
	\item[footnotesize] |\footnotesize|
	\item[normal] |\normalsize|
	\item[large] |\large|
	\item[Large] |\Large|
	\item[LARGE] |\LARGE|
	\item[huge] |\huge|
\end{itemize} 
Default is |small|.
\begin{code}
\usepackage[%
  content={text instead of an image},
  size = {huge},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{
  content={text instead of an image},
  size = {huge},%
	}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  % \includegraphics{example-image-b}
  % \caption{B}
  % \includegraphics{example-image-c}
 %  \caption{C}
\end{figure}
\end{examplebox}

\subsubsection{position}
\DescribeMacro{position}

\subsubsection{allfiguresdraft}
\DescribeMacro{allfiguresdraft}

\subsubsection{noframe}
\DescribeMacro{noframe}

\clearpage
\subsection{Individually possible}

You can also set |draft| to individual images.
\begin{codeexample}
\begin{figure}[H]
  \centering
  \includegraphics[draft]{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics[draft]{example-image-c}
  \caption{C}
\end{figure}
\end{codeexample}

\subsubsection{style}
\DescribeMacro{style}

\subsubsection{size}
\DescribeMacro{size}

\subsubsection{position}
\DescribeMacro{position}

\subsubsection{content}
\DescribeMacro{content}

\subsubsection{filename}
\DescribeMacro{filename}

@@

\section{Things to work on}

- noframe for individual image\\
- combine different styles: sc and sf etc.\\
- color frame\\
- image instead of text in background\\

>>>>

% \draftfigure --%
%            modifying drafted figures
% Copyright (c) 2017 Lukas C. Bossert
%  
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
% !TEX program = lualatex
\documentclass[a4paper,
10pt,
english
]{ltxdoc}

\input{draftfigure-preamble.tex}
\newcommand\df{draftfigure\xspace}
\newcommand\dfstring{|draftfigure|\xspace}
\setkeys{Gin}{width=.5\linewidth}

@@

\begin{multicols}{2}
\footnotesize\parskip=0mm \tableofcontents
\end{multicols}

@@

If you do not like the outcome with the filename and its path written with |\ttfamily| but still need the same size of the image in the text then use this package \dfstring to modify the outcome.
\clearpage

@@

\begin{code}
\usepackage[*@\meta{further options}@*]{draftfigure}
\end{code}
Without any further options you will now get white boxes instead of the images.
\begin{examplebox}
\begin{figure}[H]\setkeys{Gin}{draft=true}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}

@@

So let’s see some action.
\subsection{Preamble}
The following options are set in the preamble and considered globally for all figures.
\subsubsection{content}
\DescribeMacro{content}
With this option you can set an individual text which will be displayed in the white box.
\begin{code}
\usepackage[%
  content = {This figure is omitted due to missing copyrights.},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{draftfigure}{content = {This figure is omitted due to missing copyrights.}}
	\setkeys{Gin}{draft=true}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
\end{figure}
\end{examplebox}
\clearpage
\subsubsection{filename}
\DescribeMacro{filename}
Activating this option with |true| the filename will be displayed in the white box.
If you also have defined some text for |content| the filename will appear one line below of |content|.
\begin{code}
\usepackage[%
  filename,%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{filename}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
\clearpage
\DescribeMacro{filename}
\DescribeMacro{content}
And with some text in |content| it will look like this:
\begin{code}
\usepackage[%
  filename,%
  content={no image available}
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{filename,
	content={no image available}}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
\clearpage
\subsubsection{style}
\DescribeMacro{style} This defines the font style of the text of |content| or |filename|. 
You can chose one of the following styles: 
\begin{multicols}{3}
\begin{itemize}
	\item[sf] |\sffamily|
	\item[tt] |\ttfamily|
	\item[rm] |\rmfamily|
	\item[normal] |\normalfont|
	\item[bf] |\bfseries|
	\item[it] |\itshape|
	\item[sc] |\scshape|
\end{itemize}
\end{multicols}
Default is |sf|.
\DescribeMacro{content}
\DescribeMacro{style}
\begin{code}
\usepackage[%
  content={hidden image},
  style = {bf},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{style={bf},content={hidden image}}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  % \includegraphics{example-image-c}
 %  \caption{C}
\end{figure}
\end{examplebox}
\clearpage
\subsubsection{size}
\DescribeMacro{size}
You can also define the text size of |content| with predefined values: 
\begin{multicols}{2}
\begin{itemize}
	\item[tiny] |\tiny|
	\item[scriptsize] |\scriptsize|
	\item[small] |\small|
	\item[footnotesize] |\footnotesize|
	\item[normal] |\normalsize|
	\item[large] |\large|
	\item[Large] |\Large|
	\item[LARGE] |\LARGE|
	\item[huge] |\huge|
\end{itemize}
\end{multicols}
Default is |small|.
\DescribeMacro{content}
\DescribeMacro{size}
\begin{code}
\usepackage[%
  content={text instead of an image},
  size = {huge},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{
  content={text instead of an image},
  size = {huge},%
	}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
   \includegraphics{example-image-b}
   \caption{B}
  % \includegraphics{example-image-c}
 %  \caption{C}
\end{figure}
\end{examplebox}

@@

\subsubsection{position}
\DescribeMacro{position}
You can also decide where your text from |content| has to be placed
\begin{multicols}{3}
\begin{itemize}
	\item[left] |\raggedright|
	\item[center] |\centering|
	\item[right] |\raggedleft|
\end{itemize}
\end{multicols}
Default is |left|.
\DescribeMacro{content}
\DescribeMacro{position}
\begin{code}
\usepackage[%
  content={positioning},
  position = {center},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true,width=.45\linewidth}
	\setkeys{draftfigure}{
 content={positioning},
 position = {center},%
 }
  \centering
  \includegraphics{example-image-a}
  \caption{A}
   \includegraphics{example-image-b}
   \caption{B}
   \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}

\clearpage
\subsubsection{allfiguresdraft}
\DescribeMacro{allfiguresdraft}
Enabling |allfiguresdraft| all figures in your text will be shown as a white box. This is the same as |\usepackage[draft]{graphicx}|.

\subsubsection{noframe}
\DescribeMacro{noframe}
The white boxes of the replaced figures are shown with no frame and no border, but still same sizes as the figure it represents.

\subsection{Individually possible options}

Since you can also set |draft| to individual images you can also pass some of the options of \dfstring to individual images.

\DescribeMacro{style}
\DescribeMacro{size}
\DescribeMacro{position}
\DescribeMacro{content}
\DescribeMacro{filename}These are |style|, [size], |position|, |content|, |filename|.

In the preamble there is this setup
\begin{code}
\usepackage{draftfigure}
\end{code}
So no options are enabled globally.

To pass an option to an image you need to insert in the |figure|-environment the following:
\begin{code}
\setkeys{draftfigure}*@\marg{options}@*
\end{code}
or -- a little bit shorter:
\begin{code}
\setdf*@\marg{options}@*
\end{code}

The overview starts on the next page.
\clearpage 
\setkeys{Gin}{width=.4\linewidth}
\begin{codeexample}
\begin{figure}[H]
 \centering
 \setkeys{draftfigure}{content={white box}}
  \includegraphics[draft]{example-image-a}
  \caption{A}\label{A}
 \setkeys{draftfigure}{filename=true}
  \includegraphics[draft]{example-image-b}
  \caption{B}\label{B}
 \setkeys{draftfigure}{content={another white box}}
  \includegraphics[draft]{example-image-c}
  \caption{C}\label{C}
\end{figure}
\end{codeexample}
You probably noticed that I defined some text within |content| for \cref{A}.
This text is also shown for \cref{B} although I didn’t define it again --
the options you define with |\setkeys{draftfigure}|\marg{options}
are valid (in an environment) until they are refined 
as this happens for \cref{C}.

The same effect you see with the option |filename| which is enabled for \cref{B} and still valid for \cref{C}.

On the next page I show how to deactivate certain options.
\clearpage
\begin{codeexample}
\begin{figure}[H]
 \centering
 \setkeys{draftfigure}{content={white box}}
  \includegraphics[draft]{example-image-a}
  \caption{A}\label{A1}

 \setkeys{draftfigure}{filename=true,
 style={tt},position={right}}
  \includegraphics[draft]{example-image-b}
  \caption{B}\label{B1}

 \setkeys{draftfigure}{content={hidden image},
   style={rm},filename=false,position={center}}
  \includegraphics[draft]{example-image-c}
  \caption{C}\label{C1}
\end{figure}
\end{codeexample}
%Now you can see that for \cref{C1} I set |filename=false| so it isn’t shown in the white box.

\section{Things to work on}
There are still things which work not satisfactually:
\begin{itemize}
	\item  noframe for individual image
\item  combine different styles: sc and sf etc.
\item  color frame
\item  image instead of text in background
\end{itemize}
If anyone has some ideas plase let me know: \href{mailto:lukas@digitales-altertum.de}{lukas@digitales-altertum.de}
